### 2010-02-20 trunk/deliverables/D2_2_Ontology/fast_d2_2_2_ontology.tex
rearranged conceptualisation section
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@584 d8b0c59b-6544-0410-94d9-83a5658a058e

In the conceptualisation phase, we first produce a \emph{glossary of terms} which lists all classes and properties of our ontology. The glossary is seeded from the specification document (see previous section), but groups the terms according to relatedness. Also, new terms are added to this document, whereas the specification document mostly remains in its original state.

@@

@@

All properties are listed in Tab.~\ref{tab:glossary_of_terms_properties} (many of the properties covered in this table will also have an inverse).

@@

>>>>

In the conceptualisation phase, we first produce a \emph{glossary of terms} which lists all classes and properties of our ontology. After introducing the general terms, the conceptual model is then refined by relating the different terms with regards to type hierarchy, composition and aggregation.

@@

The glossary of terms is seeded from the specification document (see previous section), but groups the terms according to relatedness. Also, the evolution of the ontology is mainly reflected in this document, as new terms being introduced based on the employment and ongoing evaluation of the ontology are added here, whereas the specification document remains in its original state.

@@

All relevant properties of the FAST conceptual model are listed in Tab.~\ref{tab:glossary_of_terms_properties}. Many of the properties covered in this table will also have an inverse, which are not listed.

@@

\subsubsection{Term Relations within the Conceptual Model} % (fold)
\label{ssub:term_relations_within_the_conceptual_model}

% subsubsection term_relations_within_the_conceptual_model (end)
